### 2016-10-21 paper/evaluation.tex
cleanup initial par from eval

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from Github. We are
interested in opportunities to improve performance of test execution
with parallelism \Jbc{Should we use the term parallelism indistinctly
to refer to multi-process and multi-threaded execution?}\Mar{I think I
used the term low-level parallelism on intro to make this distiction.
Please confirm if that is correct and coherent with what you want to
say.  If yes, use this term.}, measure the
obtained gain (if any), and discuss the major concerns that affect
performance based on the obtained findings. We pose the followinga
research questions:

>>>>

We evaluated the characteristics of regression tests in
open-source development from a sample set of Java projects
from Github. We are interested in understanding the preva-
lence of long test runs, the main source of cost, and how
often developers explore parallelism to improve execution
performance. We pose the following research questions:
